Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-05-01 hpmoon-asoco.tex
fixing some typos

%That was the
                                %hypothesis of the previous
                                %paper. This paper has a new
                                %hypothesis, right? - JJ FERGU: no, this is the hypothesis of this paper (comparing adaptive with partly overlapped), but clarifying it
In order to prove this claim, our new adaptive method has been
compared against different overlapping islands schemes: a
baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a
SLA version with disjoint sections and a SLA
fixed-size overlapped version. %What was done in the previous paper?
                               %Are we re-using the results in that
                               %paper? - JJ FERGU: explained before that we are showing new results.
Different benchmark problems and different large number of islands
have been used. Results show that this new technique can improve
different quality indicators in the same amount of time when the
problem size is large.  % Shouldn't this start with "We are trying to
                        % prove..." - JJ FERGU: Already writed in previous paragraph

>>>>

%That was the
                                %hypothesis of the previous
                                %paper. This paper has a new
                                %hypothesis, right? - JJ FERGU: no, this is the hypothesis of this paper (comparing adaptive with partly overlapped), but clarifying it
In order to prove this claim, our new adaptive method has been
compared against different overlapping island schemes: a
baseline version of a distributed NSGA-II \citep{Deb00NSGAII}, a
SLA version with disjoint sections and a SLA
fixed-size overlapped version. %What was done in the previous paper?
                               %Are we re-using the results in that
                               %paper? - JJ FERGU: explained before that we are showing new results.
Different benchmark problems and different large number of islands
have been used. Results show that this new technique can improve
different quality indicators in the same amount of time when the
problem size is large.  % Shouldn't this start with "We are trying to
                        % prove..." - JJ FERGU: Already writed in previous paragraph
